---
title: "Assignment_3_2_Marketing_Promotions"
author: "Vasanthakumar Kalaikkovan"
date: "15/09/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Importing, Ploting, and Saving Data

```{r RDataLoad, echo=FALSE,include=FALSE}
# Loading Libraries
library(car) #linear regression
library(lattice) # graphics 
library(ggplot2) # graphics 

#set directory
setwd("C:/Users/vasan/Predictive-Analytics/Week 03")

df<-read.csv("dodgers.csv")
```

Head of the dataframe
```{r RHead,echo=FALSE}
head(df)
```

Summary of the dataframe
```{r RSum,echo=FALSE}
summary(df)
```

Class of the dataframe
```{r RClass,echo=FALSE}
class(df)
```

Dimension of the dataframe
```{r RDim,echo=FALSE}
dim(df)
```

Structure of the dataframe
```{r RStr,echo=FALSE}
str(df)
```

## Scatter and Box plots
```{r Rplot, echo=FALSE}
df$day_of_week<-factor(df$day_of_week,levels=c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))
df$month<-factor(df$month,levels=c("APR","MAY","JUN","AUG","SEP","OCT"))
```

```{r Rplot1, echo=FALSE}
## Day of weekdays
ggplot(df,aes(x=day_of_week,y=attend/1000))+geom_boxplot()+ggtitle("Weekdays Attendance")+
                  xlab("Days of week")+ylab("Attendances in 1000s")
```

```{r Rplot2, echo=FALSE}
## Day night attendance
ggplot(df,aes(x=day_night,y=attend/1000))+geom_boxplot()+ggtitle("Day night Attendance")+
  xlab("Day night")+ylab("Attendance in 1000s")
```

```{r Rplot3, echo=FALSE}
## Month attendance 
plot(df$month,df$attend/1000,main="Month Attendance",xlab="Month",ylab="Attendance in 1000s",las=1)
```

```{r Rplot4, echo=FALSE}
## Attendance by Temperature
ggplot(df,aes(x=month,y=attend/1000,color=fireworks))+geom_point()+facet_wrap(day_night~skies)+
  ggtitle("Attendance By Month")+xlab("Month")+ylab("Attendance in 1000s")
```


## Regression Model

```{r Regression, echo=FALSE}
#create model
my.model <- {attend ~ month + day_of_week + day_night}

#Reseed
set.seed(1234)
training_test <- c(rep(1, trunc((2/3)*nrow(df))), rep(2, trunc((1/3)*nrow(df))))

#Sample
df$Training_Test <- sample(training_test)
df$Training_Test <- factor(df$Training_Test, levels = c(1, 2), labels = c("TRAIN", "TEST"))
df.Train <- subset(df, Training_Test == "TRAIN")
df.Test <- subset(df, Training_Test == "TEST")

#Fit model to training set
train.model.fit <- lm(my.model, data = df.Train)

#Evaluate the model
df.Test$Predict_Attend <- predict(train.model.fit, newdata = df.Test)

my.model.fit <- lm(my.model, data = df)  # use all available data
print(summary(my.model.fit))

```

## Report

The multiple linear regression model is developed to find the relationship between month, day of the week, Day Night and attendance. We have found the relationship with p-value of 0.0003532. As per the above analysis would be the best to run the promotion to reach more attendance (12713). 

